### 2014-03-16 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:16	20:50:01	(Sun16.Mar)

\ai{We agree with the reviewer that this should be improved. We still state the two order of magnitude improvement over our reference implementation as this is the total improvement we obtained, but also state that this figure would likely be 5-10 had a similar effort been carried out on the CPU side as well.}

@@

\ai{Thank you providing us with this interesting reference. However, we can not see that the technique described by Chapman is relevant for us. He is not using overlapping subarrays like we do, and obtains a sparse array with associated grating lobe problems. We use of subarrays to (1) deal with the coherency problem in active sonar, and (2) to provide robustness to our covariance estimate. The latter is particularly important in our near single snapshot application. We attempt to emphasize this further in the report, and suggest [9] Kailath and Shan, "Adaptive beamforming for coherent signals and interference", as well as R.T.Hoctor and S.A.Kassam, "The unifying role of the coarray in aperture synthesis for coherent and incoherent imaging" as good reads on the subject. }

@@

\ai{Certainly. Reference added.}

@@

\begin{enumerate}
\qi{Equation (2) using a "broadside steering vector" - this is confusing... are the authors only steering at broadside? clearly not... do the authors pre-steer all of the elements prior to forming R so that can "focus" in a wideband sense?}
\ai{We indeed presteer all the elements. TODO}
%
\qi{Paragraph after equation (2) mentions "spatial averaging to avoid signal cancellation" - this problem might be better identified for readers by cit-ing the Kailath reference and using "signal cancellation due to coherent multipath".}
\ai{Thank you, both suggestions are now included.}
%
\qi{Equation 4 has second summation using index $n'$, but this index does not appear in any of the terms inside the summation.}
\ai{Good catch! Fixed.}
%
\qi{Page 2 - $\R$ is averaged over K time samples... at what rate is beamformer output produced? is $\R$ averaged using a moving window process, so that $\R[n]$ is just a rank-1 update to $\R$[n — 1] and there is one beamformer output for every input time sample?}
\ai{Actually, $\R$ is averaged over $2K+1$ time samples, this can be seen from (4). TODO}
%
\qi{Page 4, in list of three optimizations - item 3 is not self-evident, but if I understand what the authors are doing, it is described by the 1985 reference by Kailath.}
\qi{Page 4, last paragraph of 1) Arithmetic reduction - authors should iden-tify that the "Minimized memory" version skips step 2) from list of three optimization, and that the "Minimized instructions" version uses all three steps... I had a hard time understanding how the three "arithmetic reduc-tion steps" were related to the plots in Figure 5, and was puzzled about where the "minimized memory" and "minimized instruction" variants of the processing had come from. Perhaps the authors can introduce these variants more clearly and more prominently.}
\qi{On page 6, authors say "The bottleneck in the final design is now the in-version step, which is typically 5 times slower than the build step". Surely, this merits an explanation. What is the final design being compared with? What was the expectation? What changed? Figure 3 shows FLOPs before optimization - this shows build and inversion steps of roughly the same order of magnitude in the right half of the figure. Does Figure 3 set the expectation? Figure 5 shows "relative complexity reduction" of entire pro-cess, so there is no information on relative speed of build and inversion steps. Figure 10 shows estimated FLOPs for the two steps, but since both steps have different theoretical complexities (operations counts), and the two steps do not optimize the same way, this does not provide an expec-tation of the relative times.}
\qi{On page 6, authors say their implementation was improved by factor of 1.5 - 2 when run on a K20. Authors could say a few words about what a K20 is, how it differs from the Quadro 6000, that the Kepler architecture actually has features that are dramatically better for scientific computing if the code is adapted to use them (kernels can call kernels, more registers, more shared memory, ability to eliminate some host-to-GPU i/o).}
\qi{Section I says 1-2 orders of magnitude. Section IV, page 6, says 2-3 orders of magnitude.}
\qi{Reference 9 has two authors, Shan and Kailath. 11. Reference 17 seems to be the reviewed manuscript? }
\end{enumerate}

@@

\begin{enumerate}
\item Fig. 3 - Slightly increased spacing between subplots.
\item Fig. 8 - Abbreviating megapixels as "MP" in stead of "MPx".
\item Fig. 9 - Abbreviating megapixels as "MP" in stead of "MPx".
\item Fig. 11 - Abbreviating megapixels as "MP" in stead of "MPx".
\end{enumerate}

>>>>

\ai{We agree with the reviewer that this should be improved. We still state the two order of magnitude improvement over our reference implementation as this ``total payoff'' of our efforts, but also state that this figure would likely be 5-10 had the CPU side received similar treatment.}

@@

\ai{We thank the reviewer for providing this reference. However, unlike the subarray technique described by Chapman, which seems focused on reducing array complexity but in a way that causes grating lobe trouble, we use overlapping subarrays to (1) deal with the coherency problem in active sonar, and (2) to improve the rank of covariance matrix. The latter is particularly important in our case since we have hardly any temporal sample support. The Chapman reference,  distinction and a reference to [9] Kailath and Shan, "Adaptive beamforming for coherent signals and interference" is now included in the introduction to hopefully avoid future confusion.}

@@

\ai{We agree that that this paragraph lacks a reference, but feel that [9] Kailath and Shan "Adaptive beamforming for coherent signals and interference" better describes this method in the context of active sonar. The Chapman reference is added to the introduction instead.}

@@

\begin{enumerate}
\qi{Equation (2) using a "broadside steering vector" - this is confusing... are the authors only steering at broadside? clearly not... do the authors pre-steer all of the elements prior to forming R so that can "focus" in a wideband sense?}
\ai{We indeed presteer all the elements. TODO}
%
\qi{Paragraph after equation (2) mentions "spatial averaging to avoid signal cancellation" - this problem might be better identified for readers by cit-ing the Kailath reference and using "signal cancellation due to coherent multipath".}
\ai{Thank you, both suggestions are now included.}
%
\qi{Equation 4 has second summation using index $n'$, but this index does not appear in any of the terms inside the summation.}
\ai{Good catch! Fixed.}
%
\qi{Page 2 - $\R$ is averaged over K time samples... at what rate is beamformer output produced? is $\R$ averaged using a moving window process, so that $\R[n]$ is just a rank-1 update to $\R$[n — 1] and there is one beamformer output for every input time sample?}
\ai{Actually, $\R$ is averaged over $2K+1$ time samples, this can be seen from (4). TODO}
%
\qi{Page 4, in list of three optimizations - item 3 is not self-evident, but if I understand what the authors are doing, it is described by the 1985 reference by Kailath.}
\qi{Page 4, last paragraph of 1) Arithmetic reduction - authors should iden-tify that the "Minimized memory" version skips step 2) from list of three optimization, and that the "Minimized instructions" version uses all three steps... I had a hard time understanding how the three "arithmetic reduc-tion steps" were related to the plots in Figure 5, and was puzzled about where the "minimized memory" and "minimized instruction" variants of the processing had come from. Perhaps the authors can introduce these variants more clearly and more prominently.}
\qi{On page 6, authors say "The bottleneck in the final design is now the in-version step, which is typically 5 times slower than the build step". Surely, this merits an explanation. What is the final design being compared with? What was the expectation? What changed? Figure 3 shows FLOPs before optimization - this shows build and inversion steps of roughly the same order of magnitude in the right half of the figure. Does Figure 3 set the expectation? Figure 5 shows "relative complexity reduction" of entire pro-cess, so there is no information on relative speed of build and inversion steps. Figure 10 shows estimated FLOPs for the two steps, but since both steps have different theoretical complexities (operations counts), and the two steps do not optimize the same way, this does not provide an expectation of the relative times.}
\qi{On page 6, authors say their implementation was improved by factor of 1.5 - 2 when run on a K20. Authors could say a few words about what a K20 is, how it differs from the Quadro 6000, that the Kepler architecture actually has features that are dramatically better for scientific computing if the code is adapted to use them (kernels can call kernels, more registers, more shared memory, ability to eliminate some host-to-GPU i/o).}
\qi{Section I says 1-2 orders of magnitude. Section IV, page 6, says 2-3 orders of magnitude.}
\qi{Reference 9 has two authors, Shan and Kailath. 11. Reference 17 seems to be the reviewed manuscript? }
\ai{Reference 9 has been corrected. }
\end{enumerate}

@@

\begin{enumerate}
\item Fig. 3 - Slightly increased spacing between subplots.
\item Fig. 8 - Abbreviating megapixels as "MP" instead of "MPx".
\item Fig. 9 - Abbreviating megapixels as "MP" instead of "MPx".
\item Fig. 11 - Abbreviating megapixels as "MP" instead of "MPx".
\end{enumerate}
